Unsupervised embedding of trajectories captures the latent structure of discrete mobility.

### 2022-04-05 paper/current/main.tex

In the remainder of the paper, we focus on scientific mobility as a case study to interrogate the geometric space generated by the neural embedding.
In the process, we also shed light on the multi-faceted relationships between organizations.
To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
By leveraging the unique characteristics of representation learning approach, we are able to show the relationships between individual organizations, rather than aggregates such as nations or cities, this projection constitutes the largest and highest resolution ``map'' of scientific mobility to date.

>>>>

In the remainder of the paper, we focus on scientific mobility as a case study to interrogate the geometric space generated by the neural embedding.
In the process, we also shed light on the multi-faceted relationships between organizations.
To explore the topological structure of the embedding, we use a topology-based dimensionality reduction method (UMAP~\autocite{mcinnes2018umap}) to obtain a two-dimensional representation of the embedding space (Fig.~\ref{fig:projection}a).
By leveraging the unique characteristics of representation learning approach, we are able to show the relationships between individual organizations, rather than aggregates such as nations or cities, producing the largest and highest resolution ``map'' of scientific mobility to date.
